\begin{landscape}
	\small  % Switch from 12pt to 11pt; otherwise, table won't fit
	\begin{center}
		 \begin{longtable}{|p{2.2cm}||p{3.6cm}|p{3.4cm}|p{3.4cm}||p{3.8cm}|p{3.4cm}|p{3.1cm}|}
			\hline
			Provider & 
				\multicolumn{3}{c|}{Trifork} & 
				\multicolumn{3}{c|}{Rovio} \\ \cline{2-7}

			     & 
				FMK & 
				Music Festival & 
				B2B & 
				Leaderboard & 
				Virtual Wallet & 
				Ad Counter \\
			\hline
			\hline
			\endhead
			\hline \multicolumn{7}{r}{\textit{Continue on next page}} \\
			\endfoot
			\endlastfoot

			No. DCs	& 
				Currently 2. Potentially more.	& 
				Normally 1 but many could be used & 
				1 DC but many could be used & 
				1 DC but many could be used & 
				1 DC but many could be used	& 
				1 DC but many could be used \\\cline{3-3}
	
			       & 
			       & 
			     Server and all mobile devices  & 
			       & 
			       &  
			       & \\
			\hline
	
			Replication & 
				Full & 
				Full & 
				Partial. Only orders from stores relevant to the user are replicated & 
				Full & 
				Full & 
				Full \\
			\hline
	
			No. Replicas & 
				Each DC has a Riak clusters with 3 replicas of each key. In addition a datawarehouse exists with one replica & 
				Thousands & 
				Stores are replicated to all users with access to the store. This is done when the user starts the app & 
				3 within a database	& 
				3 within a database	& 
				3 within a database but copies in cache increases to thens \\
			\hline
	
			No. expected of objects & 
				Millions of medicine cards. ~2 billion auditlog entries & 
				A couple per guest. Up to 70.000 guests & 
				Millions of orders & 
				(users $/$ 30) $*$ numberLevels & 
				Tens of hundred of millions &
				Tens of thousands \\ \cline{2-5} \cline{7-7}
			
				 & 
				Millions of request-log entries and 14-day history & 
				From tens of thousands & 
				10s--100s of million of auditlog entries & 
				A game with 100 levels and 300 million users generate 1 billion objects & 
				 & 
				May increase up to hundreds of thousands \\ \cline{2-3} \cline{4-5} \cline{7-7}
	
				 & 
				Billions of audit-log entries and a few years of history & 
				To hundred of thousands &
				 & 
				Many games running at a time so hundreds or millions or billions & 
				 & 
				Many counters aggregated into a single document \\
			\hline
	
			Partitioning of data & 
				Riak shards data in 256 partitions based on consistent hashing & 
				Riak shards data in 64 partitions based on consistent hashing & 
				Riak shards data in 64 partitions based on consistent hashing & 
				No & 
				No & 
				No \\
			\hline
	
			Object sizes & 
				Medicine cards: On the order of 10KB-1MB &
				 & 
				Average 10KB & 
				150 bytes & 
				From ~ 1KB & 
				Bytes \\ \cline{2-2} \cline{4-4} \cline{6-6}
	
				 & 
				Request-log entries: On the order of 100KB & 
				 & 
				\multirow{2}{3.4cm}{Binary objects bigger and streamed in chunks of 64K} & 
				 & 
				To tens of KB & 
				 \\ \cline {2-2}
	
				 & 
				Audit-log entries: On the order of 1KB & 
				 & 
				 & 
				 & 
				 & 
				  \\
			\hline
	
			Total size of data set & 
				Medicine cards: On the order of 100GB & 
				 & 
				0.1 to 1 TB auditlogs and 10GB orders & 
				150 GB & 
				30 GB & 
				200 KB \\ \cline{2-2}
	
				 &
				Request log: On the order of 100GB & 
				 & 
				 & 
				 & 
				 & 
				  \\ \cline{2-2}
	
				 & 
				Audit log: On the order of 1TB & 
				 & 
			 	 & 
			  	 & 
			 	 & 
				  \\
			\hline
	
			Rate of growth &
				Proportional to population growth in Denmark (very low) &
				& 
				& 
				& 
				& 
				 \\ \cline{2-2}
	
				 &
				Request log: On the order of 10GB/day. Requests are deleted after 14 days & 
				 & 
			 	 & 
			 	 & 
			 	 & 
				  \\ \cline{2-2}
	
				 & 
				Audit log: On the order of 100MB/day & 
				 & 
				 & 
				 & 
				 & 
				  \\
			\hline
	
			Consistency & 
				No consistency is assumed across person IDs & 
				Eventual consistency & 
				Eventual consistency & 
				Eventual consistency & 
				\multirow{2}{3.6cm}{Lower global consistency and higher consistency within DC (Strong Consistency)} & 
				Eventual consistency \\ \cline{2-2}
	
				 & 
				Eventual consistency & 
				 & 
				 & 
				 & 
				 & 
				  \\
			\hline
				  
				Update Rate & 
				about $50/se$ &
				about $1 / min$ & 
				about $1 / sec$ & 
				 & 
				 & 
				 \\
			\hline
			
			  Conflict rate	& 
			  800 $conflicts/ day$	& 
			  none possible	& 
			  unknown & 
			   & 
			   & 
			   \\
			\hline
%		\end{tabular}
		
			\caption{Summary of values.}
			\label{tbl:metrics}
		\end{longtable}
	\end{center}
%	\end{table}
\end{landscape}