A mathematical representation of this use case is represented below.
\begin{enumerate}
	\item $M$ is the total number of \glspl{dc} and $i$ identifies one of the \glspl{dc}, $M \in \mathbb{Z}_{+}$ and $i \in \{1,\dots, M\}$.

	\item $C$ is the total number of clients and $c$ represents a client in the system, $c \in \mathbb{Z}_{+}$ and $c \in \{1,\dots, C\}$.

	\item $Balance = \{ \langle Crsytals, n1 \rangle, \langle Euro, n2 \rangle \}$ maps each currency $curr \in \{Crystals, Euro\}$ to an amount $n1, n2 \in \mathbb{R}$. $B_{ci} \in B$ keeps the balance and $\widetilde{B}_{ci} \in B$ keeps the consumed amounts of currencies by a client $c$ in \gls{dc} $i$, where $B$ denotes the set of all $Balance$ maps.

	We define the operations $\oplus$ and $\ominus$ on Balance maps $b, b' \in B$ such that: $b \oplus \langle amount \in Z, curr \in Curr \rangle = b'$ where $b'[curr] = b[curr] + amount$,  ~  $b'[cr] = b[cr]  ~ \iff  ~  cr != curr$ and $b \ominus(amount \in R, curr \in Curr) = b'$ where $b'[curr] = b[curr] - amount$,  ~  $b'[cr] = b[cr]  ~  \iff  ~  cr != curr$. We overload these operations such that they can subtract not only a tuple but a set of tuples (defined in a balance) from another balance: $b \oplus b'$ and $b \ominus b'$ where $b, b' \in B$.  
	
	\item The tuple $Voucher = \langle id, cost, spec \rangle$ defines a voucher where $id \in \mathbb{VID}$  is the voucher \gls{id}, $cost \in \mathbb{Z}_{+} \times Curr$ and $spec \in Strings$ is the details of the voucher. $V_{ci} \in V$ is a multiset of vouchers of a client $c$ kept in \gls{dc} $i$, where V denotes the set of all vouchers. Similarly, $\widetilde{V}_{ci}$ is the multiset of consumed vouchers a client $c$.
	\textcolor{red}{(Added: The cost of the voucher (Can the cost be specified in terms of different currencies?))}
	
	\item The tuple $Trans = \langle id, ts, type, args, ops \rangle$ defines a transaction where $id \in \mathbb{TID}$ is the unique transaction \gls{id}, $ts \in \mathbb{Z}_{+}$ is the timestamp, $type \in TTypes$ and $args \in Args$ is the data required for the transaction type.  $ops$ is a list of operations $o \in Ops = \{ purchasedVouc \times V, \; purchasedVCurr \times \mathbb{Z}_{+} \times Curr, \\ consumedVouc \times \mathbb{Z}_{+}, \; consumedVCurr \times \mathbb{Z}_{+} \}$ defines an operation performed in a transaction. \textcolor{red}{(Added: The list of ops in the transaction.)}
 	
	\item The tuple $W_{ci} = \langle B_{ci}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci}, T_{c} \rangle$ defines the wallet of a client $c$ kept in \gls{dc} $i$. A wallet keeps the purchased currencies, consumed currencies, purchased set of vouchers, consumed set of vouchers and the list of (not yet archived) transaction logs $T_{c}$ of a client. $|T_{c}| <= MaxTSize$ since the transaction logs in a wallet should be archived when the cardinality of the transactions reaches to the max size.

	\item The net balance of a client can be obtained by subtracting the consumed amounts of currencies from the balance of a client $c \in C$ in \gls{dc} $i$. Equation \ref{eq:balance_virtual_wallet} shows that the net amounts of all currencies should be non-negative.
	\begin{multline}  \label{eq:balance_virtual_wallet}
		\langle curr, n \rangle \in B'_{ci} = B_{ci} \ominus \widetilde{B}_{ci} \implies \\
		n \ge 0 ~ \forall ~  curr \in Curr, ~  c \in \{1,\dots, C\},  ~  i \in \{1,\dots, M\} 
	\end{multline}

	\item The net set of vouchers of a client can be obtained by subtracting the consumed vouchers from the gained vouchers of a client $c \in C$ in \gls{dc} $i$, as shown in Equation \ref{eq:balance_virtual_wallet1}, where $\setminus$ is the standard multiset difference operator.
	\begin{equation} \label{eq:balance_virtual_wallet1}
		V'_{ci} = V_{ci} \setminus \widetilde{V}_{ci} \\
	\end{equation}
  
	\item The consumed set of vouchers should be a subset of gained vouchers of a client $c$, as shown in Equation \ref{eq:balance_virtual_wallet2}.
	\begin{equation}  \label{eq:balance_virtual_wallet2}
		\widetilde{V}_{ci} \subseteq V_{ci}   
	\end{equation}
		
	\item An operation $o \in Ops$ maps a wallet $W_{ci}$ to its new contents $W'_{ci}$  $W_{ci} = \langle B_{ci}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci}, T \rangle \overset{o}{\rightarrow} W'_{ci} = \langle B'_{ci}, \widetilde{B'}_{ci}, V'_{ci}, \widetilde{V'}_{ci}, T' \rangle$ as follows: 
	
	For purchase item operation that purchases voucher $v$:
		
	$o = \langle purchasedVouc, v, curr \rangle$ where $v=\langle id, cost, spec \rangle \in V, ~ curr \in Curr$:
	
	\textcolor{red}{Additional parameter curr (which currency to use for purchasing? Can we buy a voucher using Crystals?) Does "purchased vouc" reduces balance? }
	
	As shown in Equation \ref{eq:purchaseItem_virtual_wallet}, the new contents of the wallet has: (i) the same balance (ii) the cost of the voucher $v$ added to the consumed balance (iii) the purchased voucher added to the voucher set (iv) the same set of consumed vouchers and (v) the transaction logs $T'$ that appends that purchase operation to the previous logs.	
	\begin{multline} \label{eq:purchaseItem_virtual_wallet}
		 B_{ci}[curr] > cost \implies \langle B_{ci}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci}, T \rangle ~ \overset{o}{\rightarrow} \\
	    ~ \langle B_{ci}, \widetilde{B}_{ci} \oplus \{cost, curr\}, V_{ci} \cup \{v\}, \widetilde{V}_{ci}, T' \rangle \\
	    where ~ v = \langle id, \langle cost, curr \rangle, spec \rangle \in V.
	\end{multline}
	
	For purchase virtual currency operation that purchases an $amount$ of $currency$:
	
	$o = \langle purchasedVCurr, amount, currency \rangle$ \\ 
	where $amount \in \mathbb{Z}_{+}$ and $currency \in Curr$:
	
	As shown in Equation \ref{eq:purchaseCurr_virtual_wallet}, the new contents of the wallet has: (i) the balance increased by the purchased amount of currency (ii) the same amount of consumed balance (iii) the same set of vouchers (iv) the same set of consumed vouchers and (v) the transaction logs $T'$ that appends that purchase virtual currency operation to the previous logs.	
	\begin{multline} \label{eq:purchaseCurr_virtual_wallet}
	    \langle B_{ci}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci}, T \rangle ~ \overset{o}{\rightarrow} \\
	    ~ \langle B_{ci} \oplus \{amount, curr\}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci}, T' \rangle
	\end{multline}
	
	For consume voucher operation that consumes $v$:
	
	$o = \langle consumedVouc, v \rangle$ where $v=\langle id, cost, spec \rangle  \in V$:
	
	As shown in Equation \ref{eq:consumeVouc_virtual_wallet}, the new contents of the wallet has: (i) the same balance (ii) the same amount of consumed balance (iii) the same set of vouchers (iv) the set consumed vouchers together with that recently consumed voucher $v$ and (v) the transaction logs $T'$ that appends that consume voucher operation to the previous logs.		
	\begin{multline} \label{eq:consumeVouc_virtual_wallet}
		 v \in V_{ci} \implies 
	    \langle B_{ci}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci}, T \rangle ~ \overset{o}{\rightarrow} \\
	     ~ \langle B_{ci}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci} \cup \{v\}, T' \rangle 	
	\end{multline}
	
	For consume virtual currency operation that consumes $amount$ of $currency$:
	
	$o = \langle consumedVCurr, amount \rangle$ where $amount \in \mathbb{Z}_{+}$:
	
	As shown in Equation \ref{eq:consumeVCurr_virtual_wallet}, the new contents of the wallet has: (i) the same balance (ii) the consumed balance increased by the consumed amount of currency (iii) the same set of vouchers (iv) the same set of consumed vouchers and (v) the transaction logs $T'$ that appends that consume virtual currency operation to the previous logs.
	\begin{multline} \label{eq:consumeVCurr_virtual_wallet}
	    \langle B_{ci}, \widetilde{B}_{ci}, V_{ci}, \widetilde{V}_{ci}, T \rangle ~ \overset{o}{\rightarrow} \\
	    ~ \langle B_{ci}, \widetilde{B}_{ci} \oplus \langle amount, curr \rangle, V_{ci}, \widetilde{V}_{ci}, T' \rangle 	
	\end{multline}
	
	In all these formulas, $T_{c}'=T_{c} \cup \{ \langle id, ts, type, args, o \rangle \}$, assuming the operation $o$ is the only operation performed in transaction $T_{c}$. The operations are applied in their order of appearance in the list of operations in the transaction.
\end{enumerate}